Pleiotropy of expression quantitative trait loci increases with the number of regulated genes, active cell types and tissues and bound transcription factors

### 2023-03-21 ms/ms08_figures.tex
ENH added watanabe analysis
ENH

% \begin{figure}[!tbp]
% \centering
% %
% \begin{subfigure}[]{.33\textwidth}
% \textbf{a}
% \\
% \includegraphics[width=\textwidth]{\floatRelativePath/cmpt_pleiotropic_regions.py/regions_100000_length_hist.png}
% \end{subfigure}
% %
% \begin{subfigure}[]{.33\textwidth}
% \textbf{b}
% \\
% \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_pleiotropic_regions_cumsum.py/pltbar_regions_cumsum.png}
% \end{subfigure}
% %
% \caption{Analysis of pleiotropic regions. \textbf{a}, Length distribution of pleiotropic regions. \textbf{b}, Cumulative sum ordered inversely with the number of GWAS classes.} \label{fig:pleiotropy_region_distribution}
% \end{figure}

>>>>

 \begin{figure}[!tbp]
 \centering
 %
 \begin{subfigure}[]{.33\textwidth}
 \textbf{a}
 \\
 \includegraphics[width=\textwidth]{\floatRelativePath/cmpt_pleiotropic_regions.py/100000/region_hist_100000.png}
 \end{subfigure}
 %
 \begin{subfigure}[]{.33\textwidth}
 \textbf{b}
 \\
 \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_pleiotropic_regions_cumsum.py/pltbar_regions_cumsum.png}
 \end{subfigure}
 %
 \caption{Analysis of pleiotropic regions. \textbf{a}, Length distribution of pleiotropic regions. \textbf{b}, Cumulative sum ordered inversely with the number of GWAS classes.} \label{fig:pleiotropy_region_distribution}
 \end{figure}
